Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-25 WSSSPE2_report/WSSSPE2_review.tex
Section 8: minor changes.

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open
source software, etc.
\item augment author lists to give credit to people who don't now get credit
(and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and
data)
\item developing a well-defined standard for author contribution -- what level
of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then
using social media to bring more people into the review process than is
traditional
\item determining where else software can be cited and recorded (e.g.,
acknowledgments sections of papers)
\item developing a taxonomy of contributors (e.g., Project
Credit~\cite{projectcredit}) tied to places that these metrics are already
stored (e.g., ORCID~\cite{orcid})
\item making metadata easier to add for software, creating incentive for
providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of
- simplify a way of measuring and documenting the overall credit given to an
individual over different projects
\item thinking about publishing software versus journal - software does not have to
be novel
\item determining guidelines for recommending software characteristics for
tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

@@

The following general points were initially discussed: 
\begin{itemize}
\item The FLASH~\cite{flash} project was suggested as an example of how something 
like this has been done.
\item This data could be a file that can be associated with a citation to the 
software, either through use of a DOI for the credit file, or by uploading the 
credit files as associated with the paper.
\item This idea could also be applied to data
\item This data (the credit file) should be part of the metadata that is outside
of paywalls, like citations are now.
\item It was suggested that there should also be a separate file to track
software dependencies, but this is not the same file. 
\end{itemize}

The group came up with the following actions to be performed:
\begin{enumerate}
\item Build a tool that can automatically determine who the contributors are 
(from a git or other repo), then allows the user to manually edit the output to 
add/remove people, define roles. 
\item Work with repositories to encourage them to provide the information we 
need based on what they already store.
\item Define what a citation file should look like and what it should be called.
\item Test adoption, for example, with LBNL.
\item Create credit file for a set of software.
\item Build a validator (and perhaps a visualizer) for credit files.
\item Write a tool to collect files and visualize/output interconnections (which 
software is used with which), based on an existing project.
\item When we (the group members) write papers, we should track the software 
we use, and encourage the software developers to make their software citable 
and create credit files.
\item Build a tool to export the credit file to BibTex and other citation styles.
\item Make sure the BibTex entries (exported from internal data) are somewhat 
standardized so that they can be imported into papers.  Also make sure that 
standard LaTeX style files understand and accept these entries.
\end{enumerate}

@@

A point the group considered important is that we don't want to give prizes just
to reward people who are really good at this one thing, but rather we want to
reward people who are building the culture we want as scientists.

>>>>

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open
source software, etc.
\item augment author lists to give credit to people who do not now get credit
(and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and
data)
\item developing a well-defined standard for author contribution -- what level
of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then
using social media to bring more people into the review process than is
traditional
\item determining where else software can be cited and recorded (e.g.,
acknowledgments sections of papers)
\item developing a taxonomy of contributors (e.g., Project
Credit~\cite{projectcredit}) tied to places that these metrics are already
stored (e.g., ORCID~\cite{orcid})
\item making metadata easier to add for software, creating incentive for
providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of
- simplify a way of measuring and documenting the overall credit given to an
individual over different projects
\item thinking about publishing software versus journal - software does not have to
be novel
\item determining guidelines for recommending software characteristics for
tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

@@

The following general points were initially discussed: 
\begin{itemize}
\item The FLASH~\cite{flash} project was suggested as an example of how something 
like this has been done.
\item This data could be a file that can be associated with a citation to the 
software, either through use of a DOI for the credit file, or by uploading the 
credit files as associated with the paper.
\item This idea could also be applied to data
\item This data (the credit file) should be part of the metadata that is outside
of paywalls, like citations are now. \choinote{what are ``paywalls''?}
\item It was suggested that there should also be a separate file to track
software dependencies, but this is not the same file. 
\end{itemize}

The group came up with the following actions to be performed:
\begin{enumerate}
\item Build a tool that can automatically determine who the contributors are 
(from a Git or other repository), then allows the user to manually edit the output to 
add/remove people, define roles. 
\item Work with repositories to encourage them to provide the information we 
need based on what they already store.
\item Define what a citation file should look like and what it should be called.
\item Test adoption, for example, with LBNL.
\item Create credit file for a set of software.
\item Build a validator (and perhaps a visualizer) for credit files.
\item Write a tool to collect files and visualize/output interconnections (which 
software is used with which), based on an existing project.
\item When we (the group members) write papers, we should track the software 
we use, and encourage the software developers to make their software citable 
and create credit files.
\item Build a tool to export the credit file to BibTex and other citation styles.
\item Make sure the BibTex entries (exported from internal data) are somewhat 
standardized so that they can be imported into papers.  Also make sure that 
standard LaTeX style files understand and accept these entries.
\end{enumerate}

@@

A point the group considered important is that we do not want to give prizes just
to reward people who are really good at this one thing, but rather we want to
reward people who are building the culture we want as scientists.
